Appendix

### 2018-06-08 manuscript/appendix.Rmd
improve GIS IWS-NWS plotting

```{r iws_vs_nws-gis, cache = TRUE}
lagoslakeid <- 6302
iws <- pull_iws(lagoslakeid, maxsteps = Inf)
nws <- pull_nws(lagoslakeid, maxsteps = Inf)

>>>>

```{r iws_vs_nws-gis, cache = TRUE}
# lagoslakeid <- 6302
# iws <- pull_iws(lagoslakeid, maxsteps = Inf)
# nws <- pull_nws(lagoslakeid, maxsteps = Inf)
# focal_lake <- 
# upstream_lakes <- 
# saveRDS(iws, "../data/iws_extent.rds")
# saveRDS(nws, "../data/nws_extent.rds")

iws <- readRDS("../data/iws_extent.rds")
nws <- readRDS("../data/nws_extent.rds")

iws_outline <- concaveman(st_cast(iws, "POINT"))
nws_outline <- concaveman(st_cast(nws, "POINT"))

ggplot() + 
  geom_sf(data = nws_outline, color = "cyan", size = 2) + 
  geom_sf(data = iws_outline, color = "cyan", size = 1, linetype = "dashed") + 
  geom_sf(data = nws) +
  # geom_sf(data = iws) + 
  theme_void()
